---
title: "SEM Exercise"
author: "Min Hwangbo"
date:  "`r format(Sys.Date())`"
output: 
  html_document:
    theme: paper
    highlight: pygments
    toc: true
    toc_depth: 3
    toc_float: true
    collapsed: true
    smooth_scroll: true
    number_sections: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Package & Sample data set
```{r, message = FALSE}
library(lavaan)
data("HolzingerSwineford1939") 
# Using the data set suggested by the author of the package: Yves Rosseel (Ghent Univ. from Belgium)
## Tutorial can be found on: http://lavaan.ugent.be/tutorial/tutorial.pdf
```

# Lavaan
```{r}
## Specify the model ##
HS.model <- ' visual =~ x1 + x2 + x3
              textual =~ x4 + x5 + x6
              speed =~ x7 + x8 + x9 '

# X1, X2, X3 = Visual factor measured by 3 vars
## X4, X5, X6 = Textual factor measured by 3 vars
### X7, X8, X9 = Speed factor measured by 3 vars 

## fit the model ##
fit <- cfa(HS.model, data=HolzingerSwineford1939)

## Display the summary output of the model ##
summary(fit, fit.measures=TRUE)
```

# Takeaway
Whatever the result shows strong/better fitting model, this doesn't mean that model is necessarily perfect or applicable for what I'm trying to analyze/measure. The decision has to be based on the theoretical frameworks that is considered as an evidence-based in the field that I'm interested in learning more about. i.e. for CQI building in Early Learning system, think about what are the true factors causing the "stronger" relationships between a coach and a "coachee". Is it really aobut a frequency of coaching visits, type of coaching visits, or highly competent coach/coachee relationship? Or is it about perhaps a coach can have a visit once, but the quality of the visit was holisitic enough to address performance, outcome, and process goals that are defined by International Coach Federation article on "Beyond Smart Goals (2019)" by MaryAnn McKibben Dana?
