---
title: 'Kline''s Example: Path Model'
author: "Min Hwangbo"
date: "10/9/2019"
output: 
  html_document:
    theme: paper
    highlight: pygments
    toc: true
    toc_depth: 3
    toc_float: true
    collapsed: true
    smooth_scroll: true
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm trying to figure out how to creat a Path model based on the example available on Kline's example (Kline, Figure 7.5, Table 4.2)

I'm trying to figure out how to creat a Path model based on the example available on Kline's example (Kline, Figure 7.5, Table 4.2, p. 159)

# Path Steps in R ##
```{r}
# Step 1: Load libraries
# Step 2: Input the correlations in lower diagonal form
# Step 3: Name the varibles and convert to full correlation marix
# Step 4: Display the correlations
# Step 5: Add the standard devations & convert to covariances 
# Step 6: Display the covariances
# Step 7: Specification of a model
# Step 8: Fitting the initial model to data
# Step 9: Summarize it
# Step 10: Interpret if it's fitting. If not, back to your modeling
```

# Step 1: Load libraries
```{r, message = F}
date()          # date modified
library(lavaan) # loading lavaan package
```

# Step 2: Input the correlations in lower diagonal form
```{r}
rothLower.cor <- ' 
1.00
-.03  1.00  
 .39   .07  1.00
-.05  -.23  -.13  1.00
-.08  -.16  -.29  .34   1.00 '

# important to include this ' symbol in and out
```

# Step 3: Name the varibles and convert to full correlation marix
```{r}
rothFull.cor <- getCov(rothLower.cor, names = c("exercise","hardy","fitness","stress","illness"))
```

# Step 4: Display the correlations
```{r}
rothFull.cor
```

# Step 5: Add the standard devations & convert to covariances 
```{r}
rothFull.cov <- cor2cov(rothFull.cor, sds = c(66.50, 38.00, 18.40, 33.50, 62.48)) # Adding SD & Cov conversation
```

# Step 6: Display the covariances
```{r}
rothFull.cov
```

# Step 7: Specification of a model
```{r}
# In regression format
roth.model <- '
fitness ~ exercise
stress ~ hardy
illness ~ fitness + stress'

# Unanalyzed (correlation) association btw exercise & hardy
# Automatically specified
```


# Step 8: Fitting the initial model to data
```{r}
# Variances and covariance of measured exogenous
# Variables are free parameters
# Variances calculaed with N - 1 in the denominator instead of N

model <- sem(roth.model, #calling out a model
             sample.cov=rothFull.cov, #data
             sample.nobs = 373, fixed.x = FALSE, sample.cov.rescale = FALSE) # resize, fitting, etc
```

# Step 9: Summarize it
```{r}
summary(model, fit.measures = TRUE, standardized = TRUE, rsquare = TRUE)
```

# Step 10: Interpret if it's fitting. If not, back to your modeling
```{r}
fitted(model)
residuals(model, type = "raw")
residuals(model, type = "standardized")
residuals(model, type = "cor")
modindices(model) # Careful: Chi-Squared testing: Type I error high risk group
```
