---
title: 'Kline''s Example: Path Model'
author: "Min Hwangbo"
date: "10/9/2019"
output: 
  html_document:
    theme: paper
    highlight: pygments
    toc: true
    toc_depth: 3
    toc_float: true
    collapsed: true
    smooth_scroll: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Path Steps in R ##
```{r}
# Step 1: Load libraries
# Step 2: Input the correlations in lower diagonal form
# Step 3: Name the varibles and convert to full correlation marix
# Step 4: Display the correlations
# Step 5: Add the standard devations & convert to covariances 
# Step 6: Display the covariances
# Step 7: Specification of a model
# Step 8: Fitting the initial model to dta
# Step 9: Summarize it
# Step 10: Interpret if it's fitting. If not, back to your modeling
```

# Step 1: Load libraries
```{r, message = F}
date()          # date modified
library(lavaan) # loading lavaan package
```

# Step 2: Input the correlations in lower diagonal form
```{r}
roth.Lower.cor <- ' 
1.00
-.03  1.00  
 .39   .07  1.00
-.05  -.23  -.13  1.00
-.08  -.16  -.29  .34   1.00 '

# important to include this ' symbol in and out
```

# Step 3: Name the varibles and convert to full correlation marix
# Step 4: Display the correlations
# Step 5: Add the standard devations & convert to covariances 
# Step 6: Display the covariances
# Step 7: Specification of a model
# Step 8: Fitting the initial model to dta
# Step 9: Summarize it
# Step 10: Interpret if it's fitting. If not, back to your modeling
