---
title: "Advisory Commitee Meeting"
subtitle: 1st meeting
author: "Min Hwangbo"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: tomorrow-night-bright
      highlightLines: true
      countIncrementalSlides: false
      font: Roboto
      titleSlideClass: ["center","center"]
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include = FALSE}
library(xaringanthemer)
  mono_light(
    base_color = "#4b2e83",
    code_font_google = google_font("Fira Mono"),
    header_font_google = google_font("Cabin", "700", "700i"),
    text_font_google   = google_font("Cabin", "500", "500i"),
      title_slide_background_image = "https://education.uw.edu/sites/default/files/graphics/2018/logo-transparent.png",
      title_slide_background_position = "center 500px",
      title_slide_background_size = "30%"
)#Cultivate Learning theme
```

# Welcome!

--

* Introductions & Biosketch (10-15 mins)

--

  * Career Goal

--

  * Area of Interests
  
--

* Research/Tool sharing (10 - 15 mins)

--

  * Course of Studies

--

  * Findings from Coaching to Fidelity pilot studies and Trauma Informed Care meta-analysis/literature review (SRCD posters)

--
  
* Proposal & Questions (10 mins)
  * Additional trainings/coursework/research
  * Questions from committee members

--

* Committee to discuss next steps (10 mins)

--

* Notification to student (5 mins)

---

# Dr. Gail E. Joseph (Chair)

--

* Bezos Family Distinguished Professor in Early Learning

--

* Founding Executive Director of Cultivate Learning & EarlyEdU Alliance

--

* Early learning and equity, child care quality, teacher preparation, early childhood mental health, social emotional learning, school readiness, and workforce development

--

* Recent Publication: *"The Relationship of Gross Motor and Physical Activity Environments in Child Care Settings with Early Learning Outcomes"*

---
# Dr. Sylvia S. Bagley

--

* Director of College of Education Instructional Leadership Programs

--

* Instructor for University Beyond Bars (Educational Programming & Assessment Team)

--

* Instrucational leadership, teacher preparation, trauma informed care, adult learning & coaching, data literacy & improvement, and curriculum development

--

* Recent Publication: *"Teacher Leadership in Special Education: Exploring Skills, Roles, and Perceptions"*

---
# Dr. Soojin Oh Park

--

* Assistant Professor in Early Childhood & Family Studies, Learning Sciences & Human Development, and Education, Equity, & Society Programs

--

* Affiliate Faculty of West Coast Poverty Center and Center for Studies in Demography & Ecology

--

* Public policy, mixed methods analysis, policy/program evaluation, dual language learners and immigrant-origin children, and parenting and family context of early childhood development.

--

* Recent Publication: *"Family Support of Third-Grade Reading Skills, Motivation, and Habits"*

---
# Dr. Crystal C. Hall (GSR)

--

* Associate Professor of Public Affairs in Daniel J. Evans School of Public Policy and Governance

--

* Affiliate Faculty of West Coast Poverty Center, Center for Studies in Demography & Ecology, and ideas42

--

* Social and cognitive psychology, poverty, behavioral economics, decision theory, low-income families, policy design and implementation, and organizational analysis of social policy.

--

* Recent Publication: *"Low- and Moderate-Income Tax Filers Underestimate Tax Refunds: Implications for Financial Counseling and Policy"*


---
# Min Hwangbo

--

* 2nd Year PhD Student: Learning Sciences & Human Development

--

* MEd in Education Policy; BA in Early Childhood & Family Studies; AA in Health Sciences  
--

* Project Lead & Graduate RA @ Cultivate Learning 

--

* Graduate Certificate in Demographic Methods

--

* Learning, System, Early Childhood, Coaching, Leadership, Soccer, Psychology, Evaluation, Policy, Health, Curriculum, Data, Philanthropy, Budgeting, Implementation, Intervention, Research Methods, Management, etc

--

* Pianist -> Data Collector -> Soccer Coach -> Instructor -> Preschool Teacher -> College Admin -> Tank Driver -> Policy Analyst -> Project Lead ->  ?

---
# Timeline

--

* Y1: Methodology, Theories, Learning Sciences, Lit. Review

--

* Y2: Coaching, Mixed Methods, Adult Learning, Population Study

--

* Y3 - Y4: Advanced Methods, Culture, & Dissertation

--

* Y1-4: Independent Studies
  * CA Coach Interviews
  * Implementation Fidelity
  * Trauma-Informed Care
  * Survey Development and Analysis
  * Data Integration and Visualization
  * Academic & Targeted/Technical Reporting

--

* Things to consider: Concentration? Deep dive into specialized quantitative methods? Peer-reviewed publications?

--

---
# Research Interests

--

* Theory <-> Research <-> Practice 

--

* Early Childhood System

--

* Implementation Science 

--

* Adult Learning

--

* Coaching

--

* Evaluation 

--

* Demographics

--
