---
title: "Advisory Commitee Meeting"
subtitle: "*1st*"
author: "Min Hwangbo"
date: "2018/11/29 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: tomorrow-night-bright
      highlightLines: true
      countIncrementalSlides: false
      titleSlideClass: ["center","center"]
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include = FALSE}
library(xaringanthemer)
  mono_light(
    base_color = "#4b2e83",
    code_font_google = google_font("Fira Mono"),
    header_font_google = google_font("Cabin", "700", "700i"),
    text_font_google   = google_font("Roboto", "500", "500i"),
      title_slide_background_image = "https://education.uw.edu/sites/default/files/graphics/2018/logo-transparent.png",
      title_slide_background_position = "center 500px",
      title_slide_background_size = "30%"
)#Cultivate Learning theme
```

# Welcome!

--

* Introduction

--

* Updates

--

  * R&I to Manuscript

--

  * Individual Development Plan

--

* Goal Settings

--

* Next Meeting

---
# Dr. Gail E. Joseph

---
# Dr. Sylvia S. Bagley

---
# Dr. Kathleen Artman-Meeker

---
# Dr. Soojin Oh Park

---
# Dr. Crystal C. Hall

---
# Min Hwangbo (황보 민)

--

* 2nd Year PhD Student: Learning Sciences & Human Development

--

* MEd in Education Policy; BA in Early Childhood & Family Studies; AA in Health Sciences  
--

* Project Lead & Graduate RA @ Cultivate Learning 

--

* Graduate Certificate in Demographic Methods

--

* Learning, System, Early Childhood, Coaching, Leadership, Soccer, Psychology, Evaluation, Policy, Health, Curriculum, Data, Philanthropy, Budgeting, Implementation, Intervention, Research Methods, Management, etc

--

* Pianist -> Data Collector -> Soccer Coach -> Instructor -> Preschool Teacher -> College Admin -> Tank Driver -> Policy Analyst -> Project Lead -> [R1 Postdoc Research Scientist] -> [R1 Research Associate Professor] -> ?

--

* Responsible for:

    * Summary of the program of study 
    * Summary of Research interests 
    * Summary of examination timeline

---
# Timeline

--

* Y1: Methodology, Theories, Learning Sciences, Lit. Review

--

* Y2: Coaching, Mixed Methods, CSDE Cognates, Population Study

--

* Y3: Advanced Methods, Adult Learning, Culture 

--

* Y4: Dissertation

--

* Y1-4: Independent Studies (4) - Curricular Practical Training Requirement
  * CA Coach Interviews
  * Social Emotional Learning & Implementation Fidelity
  * Trauma-Informed Care
  * Longitudinal Study
  * Survey Development and Analysis (Qualtrics)

--

* Gaps: Concentration?

--

---
# Research Interests

--

* Theory <-> Research <-> Practice 

--

* Early Childhood System

--

* Implementation Science 

--

* Adult Learning

--

* Coaching

--

* Evaluation 

--

* Demographics

--
